Lineage Analysis of CRISPR and shRNA Screens

### 2018-10-17 lineages_18Q3.Rmd

## Make drug screen boxplots
```{r}
makeDrugBoxplots <- function(drug, dataset) {
  if(dataset == "CCLE" | dataset == "ccle") {
    use_data <- filter(ccle_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- filter(ccle_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else if(dataset == "CTRP" | dataset == "ctrp") {
    use_data <- filter(ctrp_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- filter(ctrp_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else if(dataset == "GDSC" | dataset == "gdsc") {
    use_data <- filter(gdsc_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- filter(gdsc_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else { return("Error: Invalid dataset.") }

@@

```{r, eval=FALSE}
ccle_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = ccle_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
ccle_signif_lvlA <- adj_signif(ccle_signif_lvlA)
ccle_signif_lvlA <- ccle_signif_lvlA[order(ccle_signif_lvlA$p),]
saveRDS(ccle_signif_lvlA, "./data_munging/rds/ccle_signif_lvlA_gene.rds")
```

@@

# ccle_signif_genes_lvlA <- as.character(ccle_signif_lvlA$Hugo_Symbol[0:20])

@@

@@

```{r, eval=FALSE}
ctrp_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = ctrp_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
ctrp_signif_lvlA <- adj_signif(ctrp_signif_lvlA)
ctrp_signif_lvlA <- ctrp_signif_lvlA[order(ctrp_signif_lvlA$p),]
saveRDS(ctrp_signif_lvlA, "./data_munging/rds/ctrp_signif_lvlA_gene.rds")
```

@@

# ctrp_signif_genes_lvlA <- as.character(ctrp_signif_lvlA$Hugo_Symbol[0:20])

@@

@@

```{r, eval=FALSE}
gdsc_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Hugo_Symbol", "Drug"), data = gdsc_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
gdsc_signif_lvlA <- adj_signif(gdsc_signif_lvlA)
gdsc_signif_lvlA <- gdsc_signif_lvlA[order(gdsc_signif_lvlA$p),]
saveRDS(gdsc_signif_lvlA, "./data_munging/rds/gdsc_signif_lvlA_gene.rds")
```

@@

# gdsc_signif_genes_lvlA <- as.character(gdsc_signif_lvlA$Hugo_Symbol[0:20])

@@

@@

```{r fig.height=7, fig.width=12}
crispr_ptmuts_lvlA_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
crispr_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
crispr_ptmuts_lvlA_filt_color <- as.character(crispr_ptmuts_lvlA_filt$Color_Nonsilent)
names(crispr_ptmuts_lvlA_filt_color) <- crispr_ptmuts_lvlA_filt$Mutation_Status_Nonsilent

>>>>

## Wilcoxon tests by drug

```{r}
WilcoxonByDrug <- function(drug, dataset, data_name) {
  use_data <- filter(dataset, Drug == drug)
  sig <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = "Hugo_Symbol", data = use_data, method = "wilcox.test", p.adjust.method = "BH")
  sig <- adj_signif(sig)
  sig <- sig[order(sig$p),]
  sig$Drug <- drug
  sig$Dataset <- data_name
  return(sig)
}
```

## Make drug screen boxplots
```{r}
makeDrugBoxplots <- function(drug, dataset) {
  if(dataset == "CCLE" | dataset == "ccle") {
    use_data <- filter(ccle_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ccle_signif_lvlA_ByDrug[[drug]]
    # sig <- filter(ccle_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else if(dataset == "CTRP" | dataset == "ctrp") {
    use_data <- filter(ctrp_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- ctrp_signif_lvlA_ByDrug[[drug]]
    # sig <- filter(ctrp_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else if(dataset == "GDSC" | dataset == "gdsc") {
    use_data <- filter(gdsc_ptmuts_lvlA_filt, Drug == drug)
    use_color <- as.character(use_data$Color_Nonsilent)
    names(use_color) <- use_data$Mutation_Status_Nonsilent
    sig <- gdsc_signif_lvlA_ByDrug[[drug]]
    # sig <- filter(gdsc_signif_lvlA, Drug == drug)
    label_text <- data.frame(p.signif.adj = sig$p.signif.adj, Hugo_Symbol = sig$Hugo_Symbol)
    label_text <- filter(label_text, Hugo_Symbol %in% genes_lvlA_filt)
    label_text$Hugo_Symbol <- factor(label_text$Hugo_Symbol, levels = genes_lvlA_filt)
  }
  else { return("Error: Invalid dataset.") }

@@

```{r, eval=FALSE}
ccle_signif_lvlA_ByDrug <- lapply(unique(ccle_data_lvlA$Drug), WilcoxonByDrug, dataset = ccle_data_lvlA, data_name = "CCLE")
names(ccle_signif_lvlA_ByDrug) <- unique(ccle_data_lvlA$Drug)
saveRDS(ccle_signif_lvlA_ByDrug, "./data_munging/rds/ccle_signif_lvlA_ByDrug.rds")

ccle_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = ccle_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
ccle_signif_lvlA <- adj_signif(ccle_signif_lvlA)
ccle_signif_lvlA <- ccle_signif_lvlA[order(ccle_signif_lvlA$p),]
saveRDS(ccle_signif_lvlA, "./data_munging/rds/ccle_signif_lvlA_gene.rds")
```

@@

@@

```{r}
ccle_signif_lvlA_ByDrug <- readRDS("./data_munging/rds/ccle_signif_lvlA_ByDrug.rds")
ccle_signif_lvlA_ByDrug_all <- rbindlist(ccle_signif_lvlA_ByDrug, use.names = TRUE)
ccle_signif_lvlA_ByDrug_all <- ccle_signif_lvlA_ByDrug_all[order(ccle_signif_lvlA_ByDrug_all$p.adj),]

knitr::kable(ccle_signif_lvlA_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CCLE: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=FALSE}
ctrp_signif_lvlA_ByDrug <- lapply(unique(ctrp_data_lvlA$Drug), WilcoxonByDrug, dataset = ctrp_data_lvlA, data_name = "CTRP")
names(ctrp_signif_lvlA_ByDrug) <- unique(ctrp_data_lvlA$Drug)
saveRDS(ctrp_signif_lvlA_ByDrug, "./data_munging/rds/ctrp_signif_lvlA_ByDrug.rds")

ctrp_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = ctrp_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
ctrp_signif_lvlA <- adj_signif(ctrp_signif_lvlA)
ctrp_signif_lvlA <- ctrp_signif_lvlA[order(ctrp_signif_lvlA$p),]
saveRDS(ctrp_signif_lvlA, "./data_munging/rds/ctrp_signif_lvlA_gene.rds")
```

@@

@@

```{r}
ctrp_signif_lvlA_ByDrug <- readRDS("./data_munging/rds/ctrp_signif_lvlA_ByDrug.rds")
ctrp_signif_lvlA_ByDrug_all <- rbindlist(ctrp_signif_lvlA_ByDrug, use.names = TRUE)
ctrp_signif_lvlA_ByDrug_all <- ctrp_signif_lvlA_ByDrug_all[order(ctrp_signif_lvlA_ByDrug_all$p.adj),]

knitr::kable(ctrp_signif_lvlA_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "CTRP: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r, eval=FALSE}
gdsc_signif_lvlA_ByDrug <- lapply(unique(gdsc_data_lvlA$Drug), WilcoxonByDrug, dataset = gdsc_data_lvlA, data_name = "GDSC")
names(gdsc_signif_lvlA_ByDrug) <- unique(gdsc_data_lvlA$Drug)
saveRDS(gdsc_signif_lvlA_ByDrug, "./data_munging/rds/gdsc_signif_lvlA_ByDrug.rds")

gdsc_signif_lvlA <- compare_means(AUC ~ Mutation_Status_Nonsilent, group.by = c("Drug", "Hugo_Symbol"), data = gdsc_data_lvlA, method = "wilcox.test", p.adjust.method = "BH")
gdsc_signif_lvlA <- adj_signif(gdsc_signif_lvlA)
gdsc_signif_lvlA <- gdsc_signif_lvlA[order(gdsc_signif_lvlA$p),]
saveRDS(gdsc_signif_lvlA, "./data_munging/rds/gdsc_signif_lvlA_gene.rds")
```

@@

@@

```{r}
gdsc_signif_lvlA_ByDrug <- readRDS("./data_munging/rds/gdsc_signif_lvlA_ByDrug.rds")
gdsc_signif_lvlA_ByDrug_all <- rbindlist(gdsc_signif_lvlA_ByDrug, use.names = TRUE)
gdsc_signif_lvlA_ByDrug_all <- gdsc_signif_lvlA_ByDrug_all[order(gdsc_signif_lvlA_ByDrug_all$p.adj),]

knitr::kable(gdsc_signif_lvlA_ByDrug_all[, c("Hugo_Symbol", "Drug", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "GDSC: by-drug Wilcoxon test results for Level A point mutations, (BH-adjusted p-values: * p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

```{r fig.height=4, fig.width=20}
crispr_ptmuts_lvlA_filt <- filter(crispr_data_ptmuts, Hugo_Symbol %in% genes_lvlA_filt)
crispr_ptmuts_lvlA_filt$Hugo_Symbol <- ordered(crispr_ptmuts_lvlA_filt$Hugo_Symbol, levels = genes_lvlA_filt)
crispr_ptmuts_lvlA_filt_color <- as.character(crispr_ptmuts_lvlA_filt$Color_Nonsilent)
names(crispr_ptmuts_lvlA_filt_color) <- crispr_ptmuts_lvlA_filt$Mutation_Status_Nonsilent
